Inferring true changes in microbial abundance from taxonomically-biased microbiome measurements

### 2022-02-06 differential-abundance.Rmd
Change differential-abundance section title

# Taxonomic bias can cause errors in differential-abundance results {#differential-abundance}

>>>>

# DA methods vary in their robustness to bias {#differential-abundance}

<!-- # Differential-abundance methods vary in their robustness to taxonomic bias  -->

<!-- TODO: Change the GC to be about how there are various methods; state the scope that we consider; and state the punchline that they vary, with proportion-based being more sensitive. -->
